<<<<<<< HEAD
---
title: "Main Analysis"
author: "Sören Michallek"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
    toc: TRUE
    toc_depth: 2
---

*************

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(jsonlite)
library(tidyverse)
```
# Introduction

In this project I analyze and visualize the `steamdb` (Steam Video Game Database) dataset provided by [GitHub user leinstay](https://github.com/leinstay/).
The dataset can be found [here](https://github.com/leinstay/steamdb).

The dataset includes data of all currently available games on Valve's video game distribution platform [Steam](https://store.steampowered.com/). It includes prices, Steam's own categorization which describes the games genre and gameplay elements. It also includes data per game from game rating/critique sites such as [Steam Spy](https://steamspy.com/), [GameFAQs](https://gamefaqs.gamespot.com/), [Metacritic](https://www.metacritic.com/), [the International Games Data Base IGDB](https://www.igdb.com/) and [howlongtobeat (HLTB)](https://howlongtobeat.com/).

*************
# Data Import & Wrangling

We first take a look at the dataset. After importing the .json file as a list we see that as of now it includes 53981 games. Each of these games has data stored in 46 columns with one row per column.
The first goal consequently is to create an object with 46 columns and 53981 rows.

```{r}
steamdb <- as_tibble(fromJSON("steamdb.json", flatten = TRUE))
# removing irrelevant columns which contain links that will not be used for this analysis
steamdb <- steamdb %>% 
  select(-c(image | ends_with("url") | ends_with("comment")))
# creating a column for each possible platform with values TRUE or FALSE
steamdb2 <- steamdb %>% 
  mutate(Windows = str_detect("WIN"),
         Mac = str_detect("MAC"),
         Linux = str_detect("LNX")
         )
  separate(platforms, c("windows","mac","linux"))
  
# converting the price columns from cents to dollars
  
```



*************

# Data Transformation


*************

# Data Visualization
=======
---
title: "Main Analysis"
author: "Sören Michallek"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
    toc: TRUE
    toc_depth: 2
---

*************

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(jsonlite)
library(tidyverse)
```
# Introduction

In this project I analyze and visualize the `steamdb` (Steam Video Game Database) dataset provided by [GitHub user leinstay](https://github.com/leinstay/).
The dataset can be found [here](https://github.com/leinstay/steamdb).

The dataset includes data of all currently available games on Valve's video game distribution platform [Steam](https://store.steampowered.com/). It includes prices, Steam's own categorization which describes the games genre and gameplay elements. It also includes data per game from game rating/critique sites such as [Steam Spy](https://steamspy.com/), [GameFAQs](https://gamefaqs.gamespot.com/), [Metacritic](https://www.metacritic.com/), [the International Games Data Base IGDB](https://www.igdb.com/) and [howlongtobeat (HLTB)](https://howlongtobeat.com/).

*************
# Data Import & Wrangling

We first take a look at the dataset. After importing the .json file as a list we see that as of now it includes 53981 games. Each of these games has data stored in 46 columns with one row per column.
The first goal consequently is to create an object with 46 columns and 53981 rows.

```{r}
steamdb <- as_tibble(fromJSON("steamdb.json", flatten = TRUE))
# removing irrelevant columns which contain links that will not be used for this analysis
steamdb <- steamdb %>% 
  select(-c(image | ends_with("url") | ends_with("comment")))
# creating a column for each possible platform with values TRUE or FALSE
steamdb2 <- steamdb %>% 
  mutate(Windows = str_detect("WIN"),
         Mac = str_detect("MAC"),
         Linux = str_detect("LNX")
         )
  separate(platforms, c("windows","mac","linux"))
  
# converting the price columns from cents to dollars
  
```



*************

# Data Transformation


*************

# Data Visualization
>>>>>>> c7d4d4bc0b8436531b652ab5280dd61b907f96ed
